<!-- report.qmd -->

```{=typst}
#title-page(
  [The Impact of Post-2024 Federal Income Tax Changes on Hospital Workers in New York],
  [Prepared for the Greater New York Hospital Association],
  [Don Boyd],
  [Boyd Research, LLC]
)
#toc-page()
#set page(columns: 2)
```

# Introduction

some text

# Now another section

Representative households should be consistent with wage and other data on hospital workers provided by the Greater New York Hospital Association, fleshed out to reflect the diversity of tax situations households are likely to face. For example, representative households should reflect, in realistic ways, different hospital occupations, family structures, regions of the state, home ownership or renting arrangements, spousal income levels, and other factors that influence, in important ways, how recent federal income tax changes will affect federal income taxes.

Representative households should be consistent with wage and other data on hospital workers provided by the Greater New York Hospital Association, fleshed out to reflect the diversity of tax situations households are likely to face. For example, representative households should reflect, in realistic ways, different hospital occupations, family structures, regions of the state, home ownership or renting arrangements, spousal income levels, and other factors that influence, in important ways, how recent federal income tax changes will affect federal income taxes.

Representative households should be consistent with wage and other data on hospital workers provided by the Greater New York Hospital Association, fleshed out to reflect the diversity of tax situations households are likely to face. For example, representative households should reflect, in realistic ways, different hospital occupations, family structures, regions of the state, home ownership or renting arrangements, spousal income levels, and other factors that influence, in important ways, how recent federal income tax changes will affect federal income taxes.

Representative households should be consistent with wage and other data on hospital workers provided by the Greater New York Hospital Association, fleshed out to reflect the diversity of tax situations households are likely to face. For example, representative households should reflect, in realistic ways, different hospital occupations, family structures, regions of the state, home ownership or renting arrangements, spousal income levels, and other factors that influence, in important ways, how recent federal income tax changes will affect federal income taxes.

Representative households should be consistent with wage and other data on hospital workers provided by the Greater New York Hospital Association, fleshed out to reflect the diversity of tax situations households are likely to face. For example, representative households should reflect, in realistic ways, different hospital occupations, family structures, regions of the state, home ownership or renting arrangements, spousal income levels, and other factors that influence, in important ways, how recent federal income tax changes will affect federal income taxes.

# Some tables

```{r}
#| label: setup
#| output: false

library(tinytable)


```

Here are some tables

```{r}
#| label: tables
#| output: true

# head(mtcars)
# print(head(mtcars))
# tt(head(mtcars))
# print(tt(head(mtcars)), format = "typst")

tt(head(mtcars)) |>
  format_tt(markdown = TRUE) # Helps with Typst conversion

# print(tab, format = "typst")

# format_tt(
#   tab,
#   digits = 2,
#   num_mark_dec = ",",
#   num_mark_big = " ",
#   output = "typst"
# )

```
## Here is a full 2-column table

```{=typst}
#set page(columns: 1)
```
```{r}
#| label: wide-table
#| echo: false

tt(tail(mtcars)) |>
  format_tt(markdown = TRUE)  # Use 90% of full page width
```

```{=typst}
#set page(columns: 2)
```

## Now a landscape table

```{=typst}
#pagebreak()
#set page(
  flipped: true,
  columns: 1
)
```


```{r}
#| echo: false

tt(tail(mtcars)) |>
  format_tt(markdown = TRUE) 

```


```{=typst}
#pagebreak()
#set page(
  flipped: false,
  columns: 2
)
```

<!-- Import a text table -->

{{< include texttable.qmd >}}



# Back to main text

## Another subsection

### Deeper subsection

then back up to level 2

## Another level 2Level 2

Put a table here

```{=typst}
#table(
  columns: 4,
  table.header[Col 1][Col 2][Col 3][Col 4],
  [Row 1, Cell 1], [Row 1, Cell 2], [Row 1, Cell 3], [Row 1, Cell 4],
  [Row 2, Cell 1], [Row 2, Cell 2], [Row 2, Cell 3], [Row 2, Cell 4],
  // ... more rows of 4 cells
)

```

and another table here

```{=typst}
#let row2 = ([Row 2, Cell 1. This row uses a variable for each cell.],
             [Row 2, Cell 2. Edit as needed.],
             [Row 2, Cell 3. You can put paragraphs or sentences.],
             [Row 2, Cell 4. Variable example ends.])

#let cell_3_2 = [This is Row 3, Cell 2. Only this cell uses a variable.]

#table(
  columns: 4,
  table.header[Column 1][Column 2][Column 3][Column 4],
  [Row 1, Cell 1], [Row 1, Cell 2], [Row 1, Cell 3], [Row 1, Cell 4],
  ..row2,
  [Row 3, Cell 1], cell_3_2, [Row 3, Cell 3], [Row 3, Cell 4]
)

```

<!-- ```{=typst}
#colbreak()
#bibliography("references.bib", full: true, style: "apa")
``` -->

<!-- harvard-cite-them-right, ieee -->

```{=typst}
#pagebreak()
#set page(columns: 1)
```

```{=typst}
#bibliography("references.bib", title: "References", style: "apa", full: true)
```